---
title: "Housefly wing lengths"
author: "Aakash Ahuja"
date: "10/20/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The data

What does the distribution of housefly wing lengths (in mm) look like? This was apparently an important question in 1955, and the data set we look at is a famous one, from Sokal & Hunter, reproduced here:

https://seattlecentral.edu/qelp/sets/057/057.html

The data set can be scanned in from the web:

```{r}
wing.length <- scan("https://seattlecentral.edu/qelp/sets/057/s057.txt")
```

This reads the data in as a vector. To use `ggplot()`, we need the data in a data frame. The following code creates a data frame called `wings.df` that contains a variable called `Length`:

```{r}
wings.df <- data.frame(Length = wing.length)
```

We also need to load the `ggplot2` package to use the functions in it:

```{r}
library(ggplot2)
```

## Summary statistics

Find the sample mean:

```{r}
MeanWingLength<-mean(wings.df$Length)
```

**The sample mean fly wing length is 45.5 millimeters.**

Find the plug-in standard deviation and the sample standard deviation:

```{r}
# Plug-in
plugin_sd<-sqrt(mean(wings.df$Length^2) - mean(wings.df$Length)^2)
# Sample SD
sample_sd<-sd(wings.df$Length)
```

**There's hardly any difference. To one decimal place, the standard deviation of fly wing lengths is 3.9 millimeters.**

We can also describe the data using the five-number summary:

```{r}
summary(wings.df)
Q1<-quantile(wings.df$Length,0.25)
Q3<-quantile(wings.df$Length,0.75)
IQR<-Q3-Q1
median_flywings<-median(wings.df$Length)
#Finding Mode for the data.
y<-table(wings.df$Length)
names(y)[which(y==max(y))]
#Bi-Modal with mode of 45 & 46
#Also Mean=Median and almost = Mode
```

**The median fly wing length is 45.5 millimeters. The interquartile range is 5 millimeters.**

## Plot the data

Plot the empirical CDF:

```{r}
plot1<-ggplot(wings.df, aes(x = Length))
ggplot(wings.df, aes(x = Length)) + stat_ecdf() + ylab("Empirical CDF")
```

Draw a histogram:

```{r}
plot1 + geom_histogram(breaks = seq(35.5, 55.5, 1))
```

Draw a density estimate:

```{r}
plot1 + geom_density() + ylab("Estimated PDF")
```

Draw a normal quantile-quantile plot:

```{r}
ggplot(wings.df, aes(sample = Length)) + stat_qq()
```

Does the data look like it follows a normal distribution, apart from small discrepancies like rounding? **Yes The data looks like it follows a normal distribution because it closely follows a straight line. **

There's one thing about the data that might make one suspicious that the data is made up. The suspicious thing is: **The mean is exactly equal to the median(45.5). This means that the data has ZERO skewness and is perfectly symmetric data. This is oddly strange from a real world sample and suggests that the data could be made-up. **




