---
title: "Question 3"
author: "Aakash Ahuja"
date: "10/20/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The data

The Data was scanned from the official webpage of Prof. Trosset:
http://mypage.iu.edu/~mtrosset/StatInfeR/Data/sample774.dat
&nbsp;
```{r}
Question3Data<-scan("http://mypage.iu.edu/~mtrosset/StatInfeR/Data/sample774.dat")
#Converting it into a dataframe
Question3Data.df<-data.frame(Question3Data)
```

**a) The Emperical CDF:**
``` {r}
library(ggplot2)
plot3<-ggplot(Question3Data.df, aes(x = Question3Data.df$Question3Data))
plot3 + stat_ecdf() + ylab("Empirical CDF") + xlab("Data")
```

**(b) Calculate the plug-in estimates of the mean, the variance, the median, and the interquartile range.**
``` {r}
Mean_3<-mean(Question3Data.df$Question3Data)
Variance_3<-var(Question3Data.df$Question3Data)
Median_3<-median(Question3Data.df$Question3Data)
Iqr_3<-IQR(Question3Data.df$Question3Data)
```
**Mean : 1.49, Median: 1.08, Variance: 2.93, Interquartile Range:1.11**

**(c) Take the square root of the plug-in estimate of the variance and compare it to the plug-in estimate of the interquartile range. Do you think that ???x was drawn from a normal distribution? Why or why not?**
``` {r}
sd_3<-sqrt(Variance_3)
ratio_3<-Iqr_3/sd_3
```

**Ans: The ratio of IQR to Standard Deviation is 0.65 which tells that the sample is not drawn from a normal distribution. If it was drawn from a normal distribution then the ratio would have been close to 1.35**

**(d) Use the qqnorm function to create a normal probability plot. Do you think that ???x was drawn from a normal distribution? Why or why not?**
``` {r}
library(ggplot2)
qqnorm(Question3Data)
```

**Answer: No, the sample was not drawn from a normal distribution as this points do not follow the line y=x and deviate largely from it. **

**(e) Now consider the transformed sample ???y produced by replacing each x i with its natural logarithm. Do you think that ???y was drawn from a normal distribution? Why or why not?**

``` {r}
ytransformed<-log(Question3Data.df$Question3Data)
new_iqr<-IQR(ytransformed)
new_sd<-sd(ytransformed)
ratio_new<-new_iqr/new_sd
ggplot(Question3Data.df, aes(sample=log(Question3Data)))+ stat_qq()
```

**Answer: This sample after log transformation somewhat follows the line y=x and hence could be drawn from a normal distribution. When we check the ratio of IQR/SD for this new log transformed sample, it comes out to be 1.31 which is close to 1.35 indicating that it is close to a normal distribution but not exactly.**


